LAI workflow

### 2021-01-20 LAI.Rmd
First commit

```{r ll-lma-by-site, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "50%", results = "asis", fig.cap = paste0("\\label{lab-ll-lma-by-site} Species-specific Leaf lifespan vs. LMA observed for canopy leaves at two sites, shown separately. A linear model fit (line) and equation with coefficient of determination and p-value are shown separately for each site.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/leaf_cohort/lifespan_by_lma_canopy_two sites.jpeg"))
```

@@

3. Removed outliers in leaf_gm_per_m2 as those greater than 5 standard deviation by species

@@

6. Converted leaf_gm_per_m2 to LAI units as   
    leaf_fall_LAI (in m2/m2) = leaf_gm_per_m2 / LMA (in g/m2) --- (Eq 2)  
    LMA units are from Metadata_Lftraits_VariableDefinitionsOnly.doc for data in BCITRAITS_20101220.csv)

>>>>

```{r ll-lma, eval = TRUE, echo = FALSE, message = FALSE, fig.align ='center', out.width = "50%", results = "asis", fig.cap = paste0("\\label{lab-ll-lma} Species-specific Leaf lifespan vs. LMA observed for canopy leaves at two sites, shown separately. A linear model fit (line) and equation with coefficient of determination and p-value are shown separately for each site.")}
knitr::include_graphics(file.path("figures/PhenoDemoTraitsPsi/leaf_cohort/lifespan_by_lma_canopy_two sites.jpeg"))
```

@@

3. Removed outliers by species as those leaf_gm_per_m2 > 5 standard deviation

@@

6. Converted leaf_gm_per_m2 to LAI units as   
    leaf_fall_LAI (in m2/m2) = leaf_gm_per_m2 / LMA (in g/m2)
    LMA units are from Metadata_Lftraits_VariableDefinitionsOnly.doc for data in BCITRAITS_20101220.csv)
